Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-06 ms.tex
still working on goodness-of-fit discussion

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Testing }
\end{center}
\end{figure}

@@

We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
First, we considered single-MBB models with $\beta$ spatially constant (see the
black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, with 
$\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
$\beta$=1.59.

@@

@@

% discuss goodness of fit tests based on running Markov chains with different
% sets of global parameters

>>>>

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
$\chi^2_{\nu}$=$\langle \chi^2_p \rangle$ for various dust SED models.}
\end{center}
\end{figure}

@@

We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
First, we consider single-MBB models with $\beta$ spatially constant (see the
black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, 
with $\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
$\beta$=1.59. We also evaluated $chi^2_{\nu}$ for single-MBB models in which
$\beta$ varies spatially. In these cases, we used the $\beta$ map from 
\cite{planckdust}. We started by calculating $\chi^2_{\nu}$ using the 
\cite{planckdust} temperature map, finding $chi^2_{\nu}$=4.68. Note that
in this case no per-pixel chi-squared minimization was involved, as we simply 
evaluated $\chi^2_{p}$ for each pixel based on the fully-specified 
\cite{planckdust} model. % mention beta template but floating t, normalization

@@

% end with a few sentences summarizing overall takeaway(s) from this 
% goodness-of-fit analysis

@@
